Nested Stochastic Block Models Applied to the Analysis of Single Cell Data

### 2021-04-20 manuscript.tex
something on timing

Minimisation of the nSBM is a process that requires a large amount of computational resources. While the underlying \texttt{graph-tool} library is efficient in exploring the solution space using a multiflip MCMC sampling strategy, the number of required iterations before convergence is considerable and the running time scales linearly with the number of edges. Moreover, to collect a consensus partition, we minimize multiple models (default: 100) that need to be averaged. To give a reference, we collected runtimes for some example datasets in Table \ref{Table_runtime} on a commodity hardware (MacBook Air, dual core 1.6 GHz i5 processor, 16 GB RAM). Compared to Leiden approach, nSBM requires at best $\sim8\times$ times more and $\sim180\times$ times more, at worst (possibly due to limited memory for large networks).

>>>>

Minimisation of the nSBM is a process that requires a large amount of computational resources. While the underlying \texttt{graph-tool} library is efficient in exploring the solution space using a multiflip MCMC sampling strategy, the number of required iterations before convergence is considerable and the running time scales linearly with the number of edges. Moreover, to collect a consensus partition, we minimize multiple models (default: 100) that need to be averaged. To give a reference, we collected runtimes for some example datasets in Table \ref{Table_runtime} on a commodity hardware (MacBook Air, dual core 1.6 GHz i5 processor, 16 GB RAM). Compared to Leiden approach, nSBM requires at best $\sim8\times$ times more, and $\sim180\times$  at worst (possibly due to limited memory for large networks).

\textcolor{red}{Add conclusions for this paragraph}
